Appendix: Stop Lying to Me: New Visual Tools to Choose the Most Honest Nonlinear Dimension Reduction

### 2025-06-26 appendix.qmd
Figure 1 link video

```{r}
#| fig-width: 10
#| fig-height: 5
#| fig-cap: "Two projections of the \\pD{} true model overlaying the data are shown in a, b."

>>>>

```{r}
#| fig-width: 10
#| fig-height: 5
#| fig-cap: "Two projections of the \\pD{} true model overlaying the data are shown in a, b. Video of the langevitour animations is available at <https://youtu.be/35TrnYJsUUI>."
